WIDS 2024 Final Project

### 2024-01-09 Code/R FIle.qmd
started graphs for states

#### Graphing Full State Data

>>>>

#### Graphing Full State Data
##### For facets, use best judgement if by state, decade, year, or region
##### maybe make all states light grey and just choose outline outlier states and maybe regional averages

##### Party by state and year
```{r}
ggplot(full_state_data, aes(x = state_abbreviation, y = )) +
```

##### Min Wage by state and year (include fed (facet or use by decades where necessary)
# figure out spacing of graph
# can't do a line for federal minimum wage unless faceted by year instead of decade
```{r}
# abbreviation and decade
ggplot(full_state_data, aes(x = state_abbreviation)) +
  geom_point(aes(y = state_min_wage)) +
  geom_hline(aes(yintercept = fed_min_wage), color = "red") +
  facet_wrap(~decade, nrow = 5) +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "State", 
       y = "State Minimum Wage")

# region and decade
ggplot(full_state_data, aes(x = regions)) +
  geom_point(aes(y = state_min_wage)) +
  geom_hline(aes(yintercept = fed_min_wage), color = "red") +
  facet_wrap(~decade, nrow = 5) +
  labs(x = "State", 
       y = "State Minimum Wage")

# region and year
ggplot(full_state_data, aes(x = regions)) +
  geom_point(aes(y = state_min_wage)) +
  geom_hline(aes(yintercept = fed_min_wage), color = "red") +
  facet_wrap(~year, nrow = 10) +
  labs(x = "State", 
       y = "State Minimum Wage")
```

##### Adjusted Min Wage by state and year (include adjusted fed (facet or use by decades where necessary)
# figure out spacing of graph
# can't do a line for adj federal minimum wage unless faceted by year instead of decade
# add a label for the line saying federal minimum wage
```{r}
# abbreviation and decade
ggplot(full_state_data, aes(x = state_abbreviation)) +
  geom_point(aes(y = state_min_wage_2020_adj)) +
  geom_hline(aes(yintercept = fed_min_wage_2020_adj), color = "red") +
  facet_wrap(~decade, nrow = 5) +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "State", 
       y = "State Minimum Wage in 2020 Dollars")

# region and decade
ggplot(full_state_data, aes(x = regions)) +
  geom_point(aes(y = state_min_wage_2020_adj)) +
  geom_hline(aes(yintercept = fed_min_wage_2020_adj), color = "red") +
  facet_wrap(~decade, nrow = 5) +
  labs(x = "Region", 
       y = "State Minimum Wage in 2020 Dollars")

# region and year
ggplot(full_state_data, aes(x = regions)) +
  geom_point(aes(y = state_min_wage_2020_adj)) +
  geom_hline(aes(yintercept = fed_min_wage_2020_adj), color = "red") +
  facet_wrap(~year, nrow = 10) +
  labs(x = "Region", 
       y = "State Minimum Wage in 2020 Dollars")
```

##### Union employment, CB employment, and full employment (facet by decade)
# should we take the average value per decade?
# add labels for each type of employment
# fix spacing because union employment count is not visible
```{r}
# state and decade
ggplot(full_state_data, aes(x = state_abbreviation)) +
  geom_point(aes(y = employment_count), color = "red") +
  geom_point(aes(y = union_employment_count), color = "blue") +
  geom_point(aes(y = collective_bargain_employment_count), color = "green") +
  facet_wrap(~decade, nrow = 5) +
  labs(x = "State", 
       y = "Number of People Employed")

# region and decade
ggplot(full_state_data, aes(x = regions)) +
  geom_point(aes(y = employment_count), color = "red") +
  geom_point(aes(y = union_employment_count), color = "blue") +
  geom_point(aes(y = collective_bargain_employment_count), color = "green") +
  facet_wrap(~decade, nrow = 5) +
  labs(x = "Region", 
       y = "Number of People Employed")
```

##### percent union and percent collective bargaining
```{r}

```
